Neural Neural Textures Make Better Simulators ``I Can't Believe It's Not Real!''

### 2022-06-16 CORL/example.tex
minor things

	\subsection{Neural Neural Texture Projection}
		\begin{figure}[thbp]
		    \vspace{-5pt}
			\begin{center}
				\includegraphics[width=300pt]{../images/learnable_textures.pdf}
			\end{center}
			\caption{
				This figure illustrates how the neural textures are calculated in figure \ref{fig:main_diagram}. They are fully differentiable, and represented continuously along the texture's U and V axes using fourier feature networks.
			}
			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
			% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
			% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
			\label{fig:learnable_textures}
		\end{figure}

@@

	\subsection{Texture Realism Loss}
	\label{sec:texture_realism_loss}
        \vspace{-10pt}
		\begin{figure}[thbp]
			\begin{center}
				\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
			\end{center}
			\vspace{-5pt}
			\caption{
				The neural texture looks more realistic with texture realism loss enabled. Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments. 
			}
			\label{fig:texture_realism_ablation}
		\end{figure}

@@

\section{Results}\label{sec:results}

\subsection{Data}
Here I detail the datasets used in the results section. 
Every dataset has two sets of images: UVL scenes and photographs. They are all unpaired, and have RGB values ranging from 0 to 1.

@@

\subsection{Qualitative Differences}
\begin{figure}[H]
    \vspace{-30pt}
	\begin{center}
		\includegraphics[width=\textwidth]{../images/frame_inconsistency_diagram.pdf}
	\end{center}
	% Each outline color corresponds to the same cube.
	% The same cubes are marked with the same colored outlines across all photos.
	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
	\caption{
		Each row of images shows a different random placement of objects in the scene.
		Each column of images is a different image translation algorithm.
		The same cube is marked with the same color outline across all photos.
		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
		CUT and CycleGan are not consistent, while TRITON is.
		% TODO: Update the images in this to have the latest training iteration...
		}
		\label{fig:frame_inconsistency_diagram}
	\end{figure}

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/blurry_recovery.pdf}
		\end{center}
		\caption{
			The recovered texture is more crisp when we have surface consistency losses $\lUC$ and $\lTR$ enabled.
			[[TODO: include cyclegan and other algorithms here]]
		}
		\label{fig:blurry_recovery}
	\end{figure}
	% 	Alphabet Three							
	% 	Masked				Unmasked			
	% 	LPIPS		L2		LPIPS		L2	
	% 	Sync	Unsync	Sync	Unsync	Sync	Unsync	Sync	Unsync
	% Pure MUNIT	0.0437	0.0373	0.00500	0.00490	0.434	0.402	0.0425	0.0392
	% Texture Only	0.0442	0.0386	0.00586	0.00589	0.285	0.255	0.0364	0.0310
	% Texture Reality	0.0286	0.0267	0.00479	0.00478	0.117	0.1157	0.0123	0.0122
	% CycleGAN			TODO: Sync with respect to L2, so sync is always ≥ unsync					
	% CUT				TODO: Google Synthetic Dataset

@@

\subsection{Sim2real Transfer for Robot Learning}
\begin{figure}[thbp]
    \centering
    \vspace{-10pt}
    \includegraphics[width=\textwidth]{images/sim2real_framework.pdf}
    \vspace{-20pt}
    \caption{Sim2real framework of using TRITON. We evaluate in two settings: Seen and Unseen. In Unseen, we use a new camera viewpoint to train and evaluate the policy. This new viewpoint is not used for training TRITON. }
    \label{fig:sim2realframework}
\end{figure}
In this section we demonstrate how TRITON improves sim2real transfer for robot learning. To do this, we first train TRITON on a dataset consist of unpaired UVL scenes from simulator and photos from the real robot. After that, we train the robot policy in the simulator only. The input of the policy is the fake photo $\hat{p}$ translated from the simulated UVL scene using TRITON's translator $T_{A\to B}$. Finally, the trained policy is evaluated on the real robot, taking real photos $p$ as input. 
Ideally, a good image translation model leads to less gap between $p$ and $\hat{p}$, so that the policy trained on synthesized photos will transfer to real domain seamlessly.

@@

\begin{figure}[tbhp]
    \centering
    \includegraphics[width=\textwidth]{images/sim2real_res.pdf}
    \vspace{-20pt}
    \caption{Evaluation results of sim2real robot learning. We compare TRITON against two baselines and one TRITON variant w/o $\ell_{UC}$ across 3 different input image resolutions. TRITON outperforms CycleGAN~\cite{} and CUT~\cite{} consistently across (a) all resolutions and (b) Unseen viewpoints. Results in (a) are from Seen setting. Results in (b) are from 336x336 resolution. }
    \label{fig:sim2real}
\end{figure}

>>>>

	\subsection{Neural Neural Texture Projection}
		\begin{figure}[thbp]
		    \vspace{-15pt}
			\begin{center}
				\includegraphics[width=300pt]{../images/learnable_textures.pdf}
			\end{center}
			\vspace{-3pt}
			\caption{
				This figure illustrates how the our neural neural textures are calculated in figure \ref{fig:main_diagram}. They are fully differentiable, and represented continuously along the texture's U and V axes using Fourier feature networks.
			}
			\vspace{-10pt}
			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
			% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
			% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
			\label{fig:learnable_textures}
		\end{figure}

@@

	\subsection{Texture Realism Loss}
	\label{sec:texture_realism_loss}
        \vspace{-12pt}
		\begin{figure}[thbp]
			\begin{center}
				\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
			\end{center}
			\vspace{-5pt}
			\caption{
				The neural texture looks more realistic with texture realism loss enabled. Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments. 
			}
			\vspace{-10pt}
			\label{fig:texture_realism_ablation}
		\end{figure}

@@

\section{Experiments}\label{sec:results}

\subsection{Datasets}
Here we detail the datasets used in our experiments. 
Every dataset has two sets of images: UVL scenes and real photographs. They are all unpaired, and have RGB values ranging from 0 to 1.

@@

\subsection{Qualitative Evaluation Results}
\begin{figure}[thbp]
    \vspace{-30pt}
	\begin{center}
		\includegraphics[width=\textwidth]{../images/frame_inconsistency_diagram.pdf}
	\end{center}
	% Each outline color corresponds to the same cube.
	% The same cubes are marked with the same colored outlines across all photos.
	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
	\caption{
		Each row of images shows a different random placement of objects in the scene.
		Each column of images is a different image translation algorithm.
		The same cube is marked with the same color outline across all photos.
		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
		CUT and CycleGan are not consistent, while TRITON is.
		% TODO: Update the images in this to have the latest training iteration...
		}
		\label{fig:frame_inconsistency_diagram}
	\end{figure}

    \begin{figure}[thbp]
    	\begin{center}
    		\includegraphics[width=\textwidth]{../images/blurry_recovery.pdf}
    	\end{center}
    	\caption{
    		The recovered texture is more crisp when we have surface consistency losses $\lUC$ and $\lTR$ enabled.
    		[[TODO: include cyclegan and other algorithms here]]
    	}
    	\label{fig:blurry_recovery}
    \end{figure}
	% 	Alphabet Three							
	% 	Masked				Unmasked			
	% 	LPIPS		L2		LPIPS		L2	
	% 	Sync	Unsync	Sync	Unsync	Sync	Unsync	Sync	Unsync
	% Pure MUNIT	0.0437	0.0373	0.00500	0.00490	0.434	0.402	0.0425	0.0392
	% Texture Only	0.0442	0.0386	0.00586	0.00589	0.285	0.255	0.0364	0.0310
	% Texture Reality	0.0286	0.0267	0.00479	0.00478	0.117	0.1157	0.0123	0.0122
	% CycleGAN			TODO: Sync with respect to L2, so sync is always ≥ unsync					
	% CUT				TODO: Google Synthetic Dataset

@@

\subsection{Sim2real Transfer for Robot Learning}
\begin{figure}[thbp]
    \centering
    \vspace{-10pt}
    \includegraphics[width=\textwidth]{images/sim2real_framework.pdf}
    \vspace{-20pt}
    \caption{Sim2real framework of using TRITON. We evaluate in two settings: Seen and Unseen. In Unseen, we use a new camera viewpoint to train and evaluate the policy. This new viewpoint is not used for training TRITON. }
    \vspace{-5pt}
    \label{fig:sim2realframework}
\end{figure}
In this section we demonstrate how TRITON improves sim2real transfer for robot learning. To do this, we first train TRITON on a dataset consist of unpaired UVL scenes from simulator and photos from the real robot. After that, we train the robot policy in the simulator only. The input of the policy is the fake photo $\hat{p}$ translated from the simulated UVL scene using TRITON's translator $T_{A\to B}$. Finally, the trained policy is evaluated on the real robot, taking real photos $p$ as input. 
Ideally, a good image translation model leads to less gap between $p$ and $\hat{p}$, so that the policy trained on synthesized photos will transfer to real domain seamlessly.

@@

\begin{figure}[tbhp]
    \centering
    \vspace{-8pt}
    \includegraphics[width=\textwidth]{images/sim2real_res.pdf}
    \vspace{-20pt}
    \caption{Evaluation results of sim2real robot learning. We compare TRITON against two baselines and one TRITON variant w/o $\ell_{UC}$ across 3 different input image resolutions. TRITON outperforms CycleGAN~\cite{} and CUT~\cite{} consistently across (a) all resolutions and (b) Unseen viewpoints. Results in (a) are from Seen setting. Results in (b) are from 336x336 resolution. }
    \label{fig:sim2real}
    \vspace{-8pt}
\end{figure}
